On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-05-15 main.tex
typos

\begin{theorem}\label{theo:Hp}
  Suppose that $f$ satisfies $\textbf{H}_i$. There exists a non-zero
  polynomial $\Xi_{i} \in \C[S_1,\dots,S_{i-1}]$ of degree at most
  $d^{2n}$ such that if $\bm \sigma \in \C^{i-1}$ does not
  cancel $\Xi_{i}$, then $f$ and $\bm \sigma$ satisfy $\textbf{H}_i'$.
\end{theorem}
\noindent 
The proof of these theorems occupies the next two sections.

>>>>

\begin{theorem}\label{theo:Hp}
  Suppose that $f$ satisfies $\textbf{H}_i$. There exists a non-zero
  polynomial $\Xi_{i} \in \C[S_1,\dots,S_{i-1}]$ of degree at most
  $d^{2n}$ such that if $\bm \sigma \in \C^{i-1}$ does not
  cancel $\Xi_{i}$, then $f$ and $\bm \sigma$ satisfy $\textbf{H}_i'$.
\end{theorem}
\noindent 
The proof of these theorems occupies the next two sections. Some
related results appear in the literature; for instance, Lemma 5
in~\cite{JeSa10} or Proposition 4.5
in~\cite{SharpEstimatesForTheEffectiveN} are quantitative Noether
position statements. However, Theorem~\ref{theo:gen} does not follow
from these previous results. Indeed, those references would allow us
to quantify when $W(\pi_i,V(f))^\mA$ is in Noether position, whereas
we need to understand when $W(\pi_i,V(f^\mA))$ is. As we pointed out
before, these two sets are in general different.
